Diagnostics Week of June 28th

### 2020-07-07 output_scripts/Diagnostics.Rmd
can run these plots for all cohorts now
run this locally instead
update diagnostics and paper plots

---
title: "Diagnostics Week of June 28th"
author: "Owen Ward"
date: "6/30/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    code_folding: hide
---

The aim of this script is to further investigate model fit by better diagnosttic
plots for mice pairs in a specific window.

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)

@@

@@

c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"

other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
old_data_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

@@

A previous bug with C-MMHP was not correctly accounting for the degree corrected `lambda0` and corresponding
`lambda1` between each pair when interpolating the latent states and then identifying the residual matrices. 
We first want to check the effect this has.

```{r}
# output for this correction stored in output_folders/output_june_30 for c_mmhp, others haven't changed

c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"

other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

cohorts <- 1:10
cohorts <- cohorts[c(-1,-3,-5,-6,-7)] # these did not run on the cluster in time

for(current_cohort in cohorts) {
  m1_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                     "/chp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

  m2_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr <- readRDS(paste(c_mmhp_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  indep_pr <- readRDS(paste(other_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  matrix_lst_plot <- list(
                          indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                     expert_rank_10[[current_cohort]]],
                          m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]]) 
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
                    )
}

@@

To do these plots we need to compute the compensators for these models. Using the second
cohort as we have all results for it.

```{r compute diagnostics for single cohort, cache=TRUE, include=FALSE}
current_cohort <- 2
no_segments <- 500 # to run a little faster

old_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"

clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

## cmmhp ####
load(paste(c_mmhp_path, cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_", cohort_names[current_cohort],".RData",sep=''))
load(paste(c_mmhp_path,cohort_names[current_cohort],
           "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

raw_real_cmmhp_vec  <- numeric(0)
pr_real_cmmhp_vec <- numeric(0)
Lambda_cmmhp_matrix <- matrix(rep(list(),mice_number*mice_number),
                             nrow=mice_number, ncol=mice_number)

real_N_vec <- numeric(0)
#no_segments <- 500
for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
                      lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
                      alpha=mean(sim_cohort_mmhp$alpha[,pair]),
                      beta=mean(sim_cohort_mmhp$beta),
                      q1=mean(sim_cohort_mmhp$q1[,pair]),
                      q2=mean(sim_cohort_mmhp$q2[,pair]))
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        time_segment <- seq(0,current_obs_time,length.out=no_segments)
        latent_mean <- apply(interpolation_array_list[[pair]][[cur_win]],1,mean)
        latent_event <- as.numeric(apply(2-state_array_list[[pair]][[cur_win]],1,mean) > 0.5)

        ## Pearson
        est.intensity <- mmhpIntensityNumeric(params=par_est,
                                              t=current_event_time,
                                              time.vec=time_segment,
                                              latent.vec=latent_mean)
        est.intensity.events <- mmhpIntensityAtEvents(params=par_est, t=current_event_time,
                                                      latent_z=latent_event)
        all_prresidual <- sum(1/sqrt(est.intensity.events))-
          sum(sqrt(est.intensity))*(time_segment[2]-time_segment[1])
        all_Lambda <- sum(est.intensity)*(time_segment[2]-time_segment[1])

        ## rescaled interevent time
        Lambda_vec <- rep(0,length(current_event_time)+1)
        temp_time_vec <- c(0,current_event_time,current_obs_time)
        for(m in 1:(length(current_event_time)+1)){
          interevent_idx <- (time_segment>=temp_time_vec[m]) & (time_segment<temp_time_vec[m+1])
          Lambda_vec[m] <- sum(est.intensity[interevent_idx])*(time_segment[2]-time_segment[1])
        }
        real_N_vec <- c(real_N_vec, length(current_event_time))
        raw_real_cmmhp_vec <- c(raw_real_cmmhp_vec,all_Lambda)
        pr_real_cmmhp_vec <- c(pr_real_cmmhp_vec,all_prresidual)
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
      }  
      Lambda_cmmhp_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

rm(interpolation_array_list)
rm(state_array_list)

## cohort hawkes ####
raw_real_c_hawkes_vec  <- numeric(0)
pr_real_c_hawkes_vec <- numeric(0)
Lambda_c_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
                               nrow=mice_number, ncol=mice_number)

load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"event.times"][[1]]
        observe_period <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        #### update this from the stan fit
        hawkes.par <- c(model1_par_matrix$lambda0_matrix[i,j],model1_par_matrix$alpha[i,j],
                        model1_par_matrix$beta[i,j])
        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
        #                     t=current_event_time, termination = observe_period)
        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
                                                              alpha=hawkes.par[2],
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)
        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
                                                              alpha=abs(hawkes.par[2]),
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)

        ## rescaled interevent time
        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
                                           alpha=hawkes.par[2],
                                           beta=hawkes.par[3],
                                           c(0,current_event_time))
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
        raw_real_c_hawkes_vec <- c(raw_real_c_hawkes_vec,all_Lambda)
        pr_real_c_hawkes_vec <- c(pr_real_c_hawkes_vec,all_prresidual)
      }
      Lambda_c_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

## cohort degree corrected hawkes ####
raw_real_dc_hawkes_vec  <- numeric(0)
pr_real_dc_hawkes_vec <- numeric(0)
Lambda_dc_hawkes_matrix <- matrix(rep(list(),mice_number*mice_number),
                               nrow=mice_number, ncol=mice_number)

# model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

for(i in 1:mice_number){
  print(i)
  for(j in 1:mice_number){
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0&(i!=j)){
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_rescaled_interevent <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ 
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"event.times"][[1]]
        observe_period <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                                        return_df$observe.id==cur_win,"observe.time"]
        #### update this from the stan fit
        hawkes.par <- c(model2_par_matrix$lambda0_matrix[i,j],model2_par_matrix$alpha[i,j],
                        model2_par_matrix$beta[i,j])
        # hawkes.par <- optim(par=c(1,0,100), fn=uniHawkesNegLogLik, method="CG", 
        #                     t=current_event_time, termination = observe_period)
        all_Lambda <- uniHawkesIntegralIntensity(object=list(lambda0=hawkes.par[1],
                                                              alpha=hawkes.par[2],
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)
        all_prresidual <- uniHawkesPearsonResidual(object=list(lambda0=hawkes.par[1],
                                                              alpha=abs(hawkes.par[2]),
                                                              beta=hawkes.par[3]),
                                                  events=current_event_time,
                                                  termination = observe_period)

        ## rescaled interevent time
        Lambda_vec <- uniHawkesCompensator(lambda0=hawkes.par[1],
                                           alpha=hawkes.par[2],
                                           beta=hawkes.par[3],
                                           c(0,current_event_time))
        all_rescaled_interevent <- c(all_rescaled_interevent,Lambda_vec)
        raw_real_dc_hawkes_vec <- c(raw_real_dc_hawkes_vec,all_Lambda)
        pr_real_dc_hawkes_vec <- c(pr_real_dc_hawkes_vec,all_prresidual)
      }
      Lambda_dc_hawkes_matrix[i,j][[1]] <- all_rescaled_interevent
    }
  }
}

# save(raw_real_hawkes_vec, pr_real_hawkes_vec,Lambda_hawkes_matrix,
#      raw_real_mmpp_vec, pr_real_mmpp_vec, Lambda_mmpp_matrix,
#      raw_real_mmhpsd_vec, pr_real_mmhpsd_vec, Lambda_mmhpsd_matrix,
#      file = "../output/real_diag_four_models.RData")
```

This is for a specific pair in a single window, we want to plot these three models.

```{r select cohort pair window}
no_segments <- 500

@@

row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
current_event_time <- return_df[row_indicator,"event.times"][[1]]
observe_period <- return_df[row_indicator,"observe.time"]
#no_segments <- 500
time_segment <- seq(0,observe_period,length.out=no_segments)

@@

Then we can plot some of these fits.

```{r plot_functions, include=FALSE}
drawRealIntensityPaper <- function(t,
                                   object=NULL,simulation=NULL,
                                   yupper=10,add=FALSE,color=1,line.width=1,
                                 title_name="",title.cex=9, y.ratio=0,
                                 min.y=0, min.x=0, max.x=NULL, 
                                 annotate.time=FALSE,
                                 event.cex=1, box.type="l",
                                 box.col="gray40", title.line=1){
  # input object: the parameter list used for generating mmhp
  #       simulation: simulation result from simulate.mmhp 
  if(t[1]>0){
    t <- c(0,t)
  }
  if(is.null(max.x)){
    max.x <- tail(t,1)
  }
  if(is.null(object)){
    termination <- tail(t,1)
    n <- length(t)
    plot(0,0,xlim=c(min.x,max.x),ylim=c(min.y,yupper*(1+y.ratio)),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
    box(lty ='solid', col=box.col, lwd=0.7, bty=box.type)
    title(title_name,line=title.line,cex.main=title.cex)
    #left axes
    #axis(2,at=seq(0,yupper,5),labels=FALSE,cex.lab=2,lwd=0,lwd.ticks=1) 
    #text(-termination/50, y=seq(0,yupper,5), labels=seq(0,yupper,5), cex=1.6, srt=0, xpd=TRUE)
    #bottom axes
    # events
    points(t[-1],rep(min.y,n-1),cex=event.cex,pch=16,col="black")
  }else{
    state <- simulation$z
    state_time <- simulation$x
    if(tail(state_time,1)<tail(t,1)){
      state_time <- c(state_time,tail(t,1))
      state <- c(state,3-tail(state,1))
    }
    lambda0 <- object$lambda0
    lambda1 <- object$lambda1
    alpha <- object$alpha
    beta <- object$beta
    termination <- tail(t,1)
    n <- length(t)
    m <- length(state)
    if(is.null(min.y)){
      min.y <- -lambda0
    }
    if(is.null(max.x)){
      max.x <- termination
    }
    #plot(1,4,xlim=c(0.27,23),ylim=c(-0.5,9), type="n",xlab="Time",ylab="",xaxt="n",yaxt="n",cex.lab=1.8,bty="n")

@@

```{r plot intensity in a window, fig.width=10}
y.upper <- 20
title.line <- 1
title.cex <- 1
anno.cex <- 1

## Cohort Hawkes ####
# load the parameters for this pair
load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

@@

drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="Cohort Hawkes",
                       title.cex=title.cex, max.x=observe_period, box.col="black")
drawHawkesIntensityPaper(lambda0=hawkes.par[1],
                         alpha=hawkes.par[2],
                         beta=hawkes.par[3],
                         events=current_event_time, termination=observe_period)
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

#### Degree Corrected Hawkes ####
load(paste(old_data_path, cohort_names[current_cohort],
           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

@@

hawkes.par <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
                model2_par_matrix$alpha[current_i,current_j],
                model2_par_matrix$beta[current_i,current_j])

drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="Cohort DC-Hawkes",
                       title.cex=title.cex, max.x=observe_period, box.col="black")
drawHawkesIntensityPaper(lambda0=hawkes.par[1],
                         alpha=hawkes.par[2],
                         beta=hawkes.par[3],
                         events=current_event_time, termination=observe_period)
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

@@

This ouput is correctly dealing with the C-MMHP parameters now.

```{r draw_mmhp_fit}
#current_cohort <- 2
## Cohort MMHP
load(paste(c_mmhp_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
load(paste(c_mmhp_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

@@

mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
                 beta=mean(sim_cohort_mmhp$beta),
                 q1=mean(sim_cohort_mmhp$q1[,pair]),
                 q2=mean(sim_cohort_mmhp$q2[,pair]))

mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],1,function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
mmhp.est.latent <- interpolateLatentTrajectory(params=mmhp_par,events=current_event_time,zt=mmhp.est.latent,
                                               initial.state=mean(initial_state_list[[pair]][[current_win]]),
                                               termination.time=observe_period,termination.state = 2)

drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
                                       z=mmhp.est.latent$z.hat),
                       yupper=y.upper, color="black", line.width=2,
                       title_name="Cohort MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

@@

```{r, eval=FALSE}
#y.upper <- 10
#title.line <- 1
#title.cex <- 0.1
drawRealIntensityPaper(current_event_time, object=mmhp_par,title.line=title.line,
                       simulation=list(x=c(0,mmhp.est.latent$x.hat),
                                       z=mmhp.est.latent$z.hat),
                       yupper=y.upper, color="black", line.width=2,
                       title_name="MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")
mtext(side=1, text="Time", line=1.6, cex=anno.cex)
mtext(side=2, text="Intensity", line=1.2, cex=anno.cex)

@@

The corresponding QQ plots also.

```{r, eval=FALSE}
anno.cex <- 1
#### Hawkes
Lambda.hawkes.test <- Lambda_hawkes_matrix[current_i,current_j][[1]]

p <- ppoints(length(Lambda.hawkes.test))    # 100 equally spaced points on (0,1), excluding endpoints
q <- quantile(Lambda.hawkes.test,p=p,na.rm=TRUE) # percentiles of the sample distribution
plot(qexp(p),q, 
     xlab="",ylab="",xaxt="n",yaxt="n",
     pch=1,cex=1,col="Black",ylim=c(0,8),xlim=c(0,5))
mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:8),cex.axis=1,lwd=0,lwd.ticks=1)
qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)

#### mmhp
Lambda.test.mmhp <- Lambda_mmhp_matrix[current_i,current_j][[1]]
p <- ppoints(length(Lambda.test.mmhp))    # 100 equally spaced points on (0,1), excluding endpoints
q <- quantile(Lambda.test.mmhp,p=p,na.rm=TRUE) # percentiles of the sample distribution
plot(qexp(p),q, 
     xlab="",ylab="",xaxt="n",yaxt="n",
     pch=1,cex=1,col="Black",ylim=c(0,max(q)),xlim=c(0,3))
mtext(side=1, text="Theoretical Quantiles", line=1.6, cex=anno.cex)
mtext(side=2, text="Empirical Quantiles", line=1.2, cex=anno.cex)
Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)
```

>>>>

---
title: "Diagnostics Week of June 28th"
author: "Owen Ward"
date: "6/30/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

<!-- The aim of this script is to further investigate model fit  -->
<!-- by better diagnostic -->
<!-- plots for mice pairs in a specific window. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

data_path <- "../output/"

@@

# c_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_june30/"
# 
# other_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"
# old_data_path  <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_null_windows/"

@@

A previous bug with C-MMHP was not correctly accounting for the degree 
corrected `lambda0` and corresponding
`lambda1` between each pair when interpolating the latent states and then 
identifying the residual matrices. This gives more reasonable results for
overall model fit in terms of the total Pearson residuals summed across all 
observation windows.

```{r}
cohorts <- 1:10

for(current_cohort in cohorts) {
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                     "/chp_pr_matrix_",cohort_names[current_cohort],
                     ".RDS",sep=''))

  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  matrix_lst_plot <- list(
                          indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                     expert_rank_10[[current_cohort]]],
                          m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                          m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]]) 
  cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
                    )
}

@@

```{r test pairs, include=FALSE,eval=FALSE}
current_cohort <- 1

clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

best_i <- top_pairs$initiator[1]
best_j <- top_pairs$recipient[1]
wind <- unlist(lapply(top_pairs$no.events,which.max))[1]

```{r select cohort pair and window,eval=FALSE,include=FALSE}
no_segments <- 500

@@

row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
current_event_time <- return_df[row_indicator,"event.times"][[1]]
observe_period <- return_df[row_indicator,"observe.time"]
time_segment <- seq(0,observe_period,length.out=no_segments)

@@

```{r plot_functions, include=FALSE, cache=TRUE}
drawRealIntensityPaper <- function(t,
                                   object=NULL,simulation=NULL,
                                   yupper=10,add=FALSE,color=1,line.width=1,
                                 title_name="",title.cex=9, y.ratio=0,
                                 min.y=0, min.x=0, max.x=NULL, 
                                 annotate.time=FALSE,
                                 event.cex=1, box.type="l",
                                 box.col="gray40", title.line=1){
  # input object: the parameter list used for generating mmhp
  #       simulation: simulation result from simulate.mmhp 
  if(t[1]>0){
    t <- c(0,t)
  }
  if(is.null(max.x)){
    max.x <- tail(t,1)
  }
  if(is.null(object)){
    termination <- tail(t,1)
    n <- length(t)
    plot(0,0,xlim=c(min.x,max.x),ylim=c(min.y,yupper*(1+y.ratio)),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
    box(lty ='solid', col=box.col, lwd=0.7, bty=box.type)
    title(title_name,line=title.line,cex.main=title.cex)
    #left axes
    #axis(2,at=seq(0,yupper,5),labels=FALSE,cex.lab=2,lwd=0,lwd.ticks=1) 
    #text(-termination/50, y=seq(0,yupper,5), labels=seq(0,yupper,5), cex=1.6, srt=0, xpd=TRUE)
    #bottom axes
    # events
    points(t[-1],rep(min.y,n-1),cex=event.cex,pch=16,col="black")
  }else{
    state <- simulation$z
    state_time <- simulation$x
    if(tail(state_time,1)<tail(t,1)){
      state_time <- c(state_time,tail(t,1))
      state <- c(state,3-tail(state,1))
    }
    lambda0 <- object$lambda0
    lambda1 <- object$lambda1
    alpha <- object$alpha
    beta <- object$beta
    termination <- tail(t,1)
    n <- length(t)
    m <- length(state)
    if(is.null(min.y)){
      min.y <- -lambda0
    }
    if(is.null(max.x)){
      max.x <- termination
    }
    #plot(1,4,xlim=c(0.27,23),ylim=c(-0.5,9), type="n",xlab="Time",ylab="",xaxt="n",yaxt="n",cex.lab=1.8,bty="n")

@@

```{r extract hawkes fits, results='hide',eval=FALSE,include=FALSE}
print(current_cohort)

## Cohort Hawkes ####
# load the parameters for this pair
load(paste(data_path, cohort_names[current_cohort],
           "/cohort_hp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

@@

#### Degree Corrected Hawkes ####
load(paste(data_path, cohort_names[current_cohort],
           "/cohort_dchp_stan_result_", cohort_names[current_cohort],".RData",sep=''))

@@

hawkes.par_dc <- c(model2_par_matrix$lambda0_matrix[current_i,current_j],
                model2_par_matrix$alpha[current_i,current_j],
                model2_par_matrix$beta[current_i,current_j])

@@

```{r extract_cmmhp_fit, results='hide',eval=FALSE,include=FALSE}
print(current_cohort)
## Cohort MMHP
load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

@@

c_mmhp_par <- list(lambda1=mean(sim_cohort_mmhp$lambda1[,pair]),
                 lambda0=mean(sim_cohort_mmhp$lambda0[,pair]),
                 alpha=mean(sim_cohort_mmhp$alpha[,pair]),
                 beta=mean(sim_cohort_mmhp$beta),
                 q1=mean(sim_cohort_mmhp$q1[,pair]),
                 q2=mean(sim_cohort_mmhp$q2[,pair]))

c_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
                                1,
                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
c_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
                                               events=current_event_time,
                                                       zt=c_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
                     termination.time=observe_period,
                     termination.state = 2)

@@

```{r extract indep mmhp fit, results='hide',eval=FALSE,include=FALSE}

print(current_cohort)
#### I-MMHP  ####
load(paste(data_path,cohort_names[current_cohort],
             "/sep_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
             "/mmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))

sep_mmhp_par <- list(lambda1=mean(sim_mmhp_sep$lambda1[,pair]),
                 lambda0=mean(sim_mmhp_sep$lambda0[,pair]),
                 alpha=mean(sim_mmhp_sep$alpha[,pair]),
                 beta=mean(sim_mmhp_sep$beta),
                 q1=mean(sim_mmhp_sep$q1[,pair]),
                 q2=mean(sim_mmhp_sep$q2[,pair]))

sep_mmhp.est.latent <- ifelse(apply(state_array_list[[pair]][[current_win]],
                                1,
                                function(x) sum(x==1)) >500,rep(1,1000),rep(2,1000))
sep_mmhp.est.latent <- interpolateLatentTrajectory(params=c_mmhp_par,
                                               events=current_event_time,
                                                       zt=sep_mmhp.est.latent,                                         initial.state=mean(initial_state_list[[pair]][[current_win]]),
                     termination.time=observe_period,
                     termination.state = 2)

@@

For each cohort, we extract the mouse pair with the most interactions, plotting
thes estimated intensity in the window with the most interactions along with
the QQ plot of all events (in all windows) between that pair.

```{r pair diagnostic plot, include=FALSE,eval=FALSE}
row_indicator <- return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win
row_idx <- which(return_df$initiator==current_i&return_df$recipient==current_j&return_df$observe.id==current_win)
current_event_time <- return_df[row_indicator,"event.times"][[1]]
observe_period <- return_df[row_indicator,"observe.time"]
no_segments <- 500
time_segment <- seq(0,observe_period,length.out=no_segments)

par(mfrow=c(2,4), oma=c(1,1,1,1), mar=c(2,3,2,1), mgp=c(0.8,0,0))
layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
anno.cex <- 1.3
title.cex <- 2.2
title.line <- 0.5
y.upper <- 20

#### Cohort Hawkes  ####

drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="C-HP",
                       title.cex=title.cex, max.x=observe_period, box.col="black")
drawHawkesIntensityPaper(lambda0=hawkes.par[1],
                         alpha=hawkes.par[2],
                         beta=hawkes.par[3],
                         events=current_event_time, termination=observe_period)

### DC Cohort Hawkes ####

drawRealIntensityPaper(current_event_time,
                       yupper=y.upper, color="black",line.width=2,title.line=title.line,
                       title_name="DC-HP",
                       title.cex=title.cex, max.x=observe_period, box.col="black")
drawHawkesIntensityPaper(lambda0=hawkes.par_dc[1],
                         alpha=hawkes.par_dc[2],
                         beta=hawkes.par_dc[3],
                         events=current_event_time, termination=observe_period)

#### DC C-MMHP ####
drawRealIntensityPaper(current_event_time, object=c_mmhp_par,title.line=title.line,
                       simulation=list(x=c(0,c_mmhp.est.latent$x.hat),
                                       z=c_mmhp.est.latent$z.hat),
                       yupper=y.upper, color="black", line.width=2,
                       title_name="DC C-MMHP", title.cex=title.cex, max.x=observe_period, box.col="black")

#### Sep MMHP ####
